signalHsmm - a novel semi-Markov model of eukaryotic signal peptides

### 2015-06-17 paper.tex
added MCC

Amino acids were clustered using several criteria relevant for the architecture of signal peptide: hydrophobicity, frequency in alpha-helices, polarity and size. High values of hydrophobicity are required in the h-region, the core of signal peptides. Alpha-helix, the secondary structure of this region, is probably induced by the positively charged n-region. Polarity as well as size are important especially in the cleavage site~\citep{1994palzkillselection}.

@@

We selected 13 properties from AAIndex database~\citep{2008kawashimaaaindex} (see Table~\ref{tab:aaprop}), each attributed to a single criterion. Considering all combinations of single properties for every criterion, we created 96 possible clusterings of amino acids using Euclidean distance and Ward's method.

@@

The advantage of HSMM model is not only a better performance but also, as 
model structure (see figure~\ref{fig:model_hsmm}) is straightforward, easier interpretation 
for researcher without mathematical background.

@@

\begin{figure}[ht]\centering
\includegraphics[width=0.9\textwidth]{figures/cvres.png}
\caption{}
\label{fig:cvres}
\end{figure}

>>>>

Amino acids were clustered using several criteria relevant for the architecture of signal peptide: hydrophobicity, frequency in alpha-helices, polarity and size. High hydrophobicity is a determinant of the h-region, the core of signal peptides. Alpha-helix, the secondary structure of the h-region, is probably induced by the positively charged n-region. High polarity as well as smaller size are important features of the residues in the cleavage site~\citep{1994palzkillselection}.

@@

We selected 13 properties from AAIndex database~\citep{2008kawashimaaaindex} (see Table~\ref{tab:aaprop}), each attributed to a single criterion. We created 96 permutations of the properties, where each permutation contains only one property associated with a given criterion. Considering all permutations of properties, we created 96 possible clusterings of amino acids using Euclidean distance and Ward's method. Further, we cut the clusterings to create four-group encodings.

\begin{figure}[ht]\centering
\includegraphics[width=0.9\textwidth]{figures/cvres.png}
\caption{Results of cross-validation. 1. An encoding providing the best sensitivity (AUC = 0.9346, MCC = 0.6479). 3. An encoding providing the best specificity (AUC = 0.9687, MCC = 0.8689).}
\label{fig:cvres}
\end{figure}

@@

The advantage of HSMM model is not only a better performance but also, as 
model structure (see figure~\ref{fig:hsmm}) is straightforward, easier interpretation 
for researcher without mathematical background.

@@
